Identifying Drawings with the Quick Draw Challenge

### 2018-12-07 report/report_draft.Rmd
changed wording and converted to latex

>>>>

Many recent industry innovations have included neural networks. An important 
research area within neural networks has been image classification. One of 
the best techniques to classify images is Convolutional Neural Networks (CNN).
We have sought to better understand industry best practices by exploring 
different image classification techniques with neural networks. Our 
exploration starts by manually performing image classification and noting the 
level of human accuracy. We then use a fully connected neural network to 
perform image classification before implementing a CNN. We implemented options
for tuning and debugging the neural network while implementing each method 
during our process. We were able to develop an intuition for image 
classification best practices using neural networks after our research.

Many supervised machine learning methods often differ from those employed 
when constructing neural networks. These supervised machine learning methods, 
such as logistic regression or decision tree classification, require feature 
engineering to successfully classify an image. Models requiring feature 
engineering rely on considerable effort by subject matter experts to achieve 
reasonable accuracy. Neural networks allow for an approach which does not 
require feature engineering to achieve similar or better accuracy. Industry 
engineering efforts regarding feature engineering can be shifted to neural 
networks  in some cases such as image classification. Moreover, the 
availability of cheap computing resources sped up a shift towards the use of 
neural networks.

When considering modeling approaches, we consider both fully connected and 
convolutional neural networks. A fully connected neural network is known to 
be inefficient at classifying large images. These inefficiencies in a fully 
connected neural network partly arise because every neuron in the $n-1$ layer 
must be connected to the $n$th layer.
